Eye in a Disk: eyeIntegration human pan-eye and body transcriptome database version 1.00

### 2019-02-21 manuscript.Rmd
improve coords

retina_plus_group <- tsne_50 %>% filter(X1 > -5, X1 < 40, X2 > 30, X2 < 40)
dbscan_cluster <- dbscan(retina_plus_group %>%  select(X1, X2) ,  minPts = 3, eps = 2)

>>>>

retina_plus_group <- tsne_50 %>% filter(X1 > 17, X1 < 50, X2 < -15, X2 > -50)
retina_plus_group <- bind_rows(retina_plus_group, tsne_50 %>% filter(X1 > 35))
dbscan_cluster <- dbscan(retina_plus_group %>%  select(X1, X2) ,  minPts = 3, eps = 2)
